%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref, textcomp, lipsum}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
}
\usepackage[left=0.5in,top=0.5in,right=0.6in,bottom=0.5in]{geometry} % 

\name{Arun Palaniappan Thiagarajan}
\address{\textit{\href{mailto:arunp.psg@gmail.com}{arunp.psg@gmail.com} \\ \href{https://www.linkedin.com/in/arun-palaniappan-tr/}{LinkedIn} \\ \href{https://github.com/arunpalaniappan}{Github} \\ \href{https://arunpalaniappan.github.io/}{Webpage}}} % Your phone number and email

\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
\vspace*{0.1in}
{\bf PSG College of Technology, Coimbatore} \hfill {July '16 - Present} \\ {\emph{MSc Data Science} (Integrated  five year program)} \\
CGPA (upto $8^{th}$ semester): 9.02/10
\end{rSection}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Experience}
\vspace*{0.1in}
{\bf \href{https://arunpalaniappan.github.io/files/FCI.pdf}{Data Driven Analysis of FCI’s Operations and Recommendations}} { \hfill May `20 - October `20}\\
\textit{Working paper with Shamshu Dharwez, Nehal Muthu}
\begin{itemize}
\item We collected available open data, studied operations of Food Corporation of India and found gaps in allotment and offtake of Indian states.
\item We found factors which influence states proposals, efficient utilization of foodgrains, challenges in providing food security under the current system and suggested policy recommendations.
\end{itemize}

{\bf TCS Research} { \hfill May `19 - October `19}\\
\textit{Research Intern under \href{https://www.linkedin.com/in/sharadha-ramanan-43bb4946/}{Sharadha Ramanan}}{\hfill Chennai}
\begin{itemize}
\item Studied dynamic pricing of interdependent and perishable product using reinforcement learning techniques.
\item Proposed a Q-learning model which achieved a yield of 16\% higher than passive pricing techniques in simulated environment.
\end{itemize}
\end{rSection}
\begin{rSection}{Key Projects}
\vspace*{0.1in}
{ \bf \href{https://github.com/arunpalaniappan/Handwriting-Recognition-using-Tensorflow}{Intelligent Character Recognition using Tensorflow}} {\hfill June 2020}
\begin{itemize}
\item Used IAM dataset and augmented the dataset with noise added data points to build a robust convolutional netural network to recognize handwritted words.
\item Performed gradient clipping, used $l_{\infty}$-norm loss and achieved an accuracy of 44\%.
\end{itemize}

{\bf \href{https://github.com/arunpalaniappan/resume-parser}{Resume Parser}} {\hfill Febraury 2020}
\begin{itemize}
\item Extracted email-id, skill set, phone number, educational qualifications and experiences from a resume using regex based techniques with text preprocessing.
\item Found relevance of resume to the position applied by using document similarity metrics.
\end{itemize}

{\bf \href{https://github.com/arunpalaniappan/budget-analyzer}{Budget Analyzer}}{\hfill March 2019}
\begin{itemize}
\item Built an application to keep track of users income and expenses using MongoDb for backend and PyQt for front end.  The application gives prediction for future expenses using time-series analysis.
\end{itemize}

{\bf \href{https://github.com/arunpalaniappan/Decoding-raw-EEG-signals}{Decoding Motor-movement from EEG signals}} {\hfill October 2018}
\begin{itemize}
\item Studied the use of support vector machines and explored mutliple kernel based support vector machines for decoding raw EEG signals into motor movements
\item Used data from BCI Competition IV and achieved an accuracy of 60\%.
\end{itemize}

\end{rSection}

\pagebreak

\begin{rSection}{Relevant Courses}
\begin{itemize}[leftmargin=*]
\itemsep -0.5em 
\item \textbf{Computer Science} - Data Structures, Design and Analysis of Algorithms, Database Systems, Data Mining, Supervised and Unsupervised Learning, Reinforcement Learning.
\item \textbf{Mathematics} - Calculus and its Applications, Theory of Probability, Applied Statistics, Graph Theory, Stochastic Models, Predictive Analytics, Linear Algebra, Network Science\footnotemark[1], Game Theory\footnotemark[1]
\footnotetext[1]{Courses currently undertaking}
\end{itemize}
\end{rSection}

\begin{rSection}{Academic Interests}
Machine Learning, Economics, Network Science
\end{rSection}

\begin{rSection}{Technical Skills}
\begin{itemize}[leftmargin=*]
\itemsep -0.5em 
\item \textbf{Strong} - Python, Rstudio
\item \textbf{Familiar} - MATLAB, C/C++, MySQL
\item \textbf{Tools} - Pytorch, Git, \LaTeX
\end{itemize}
\end{rSection}

\begin{rSection}{Academic Service}
\vspace*{0.1in}
\begin{itemize}[leftmargin=*]
\item Led the development of \href{https://groups.google.com/g/psg-ml-seminar}{Machine Learning study group} at PSG College of Technology and organized weekly online meetings to discuss machine learning papers and concepts.
\item Conducted Cricket and Statistics program and \href{https://themango.co/programs/excel-with-sports/}{Excel for Sports} at Mango Education for kids aged between 11 - 15.
\end{itemize}
\end{rSection}

\begin{rSection}{Extracurriculars and Achievements}
\vspace*{0.1in}
\begin{itemize}[leftmargin=*]
\item Participated virtually in \href{https://simons.berkeley.edu/workshops/rl-2020-bc}{Theory of Reinforcement Learning Boot Camp} organized by Simons Institute for Theory of Computing.
\item A member of Coimbatore Toastmasters Club between 2017-2019 and served as Secretary of the club between July 2018-Dec 2018.
\item Wrote my study notes on multi-arm bandits as blogs at \href{https://arunpalaniappan.github.io/}{https://arunpalaniappan.github.io/}
\item Secured Fifth rank in maths olympiad organized by Department of Mathematics, PSG College of Technology.
\item Obtained Finisher medal in Amma marathon conducted by government of Tamil Nadu for cancer awareness at Coimbatore.
\end{itemize}
\end{rSection}

\begin{rSection}{References}
\begin{itemize}[leftmargin=*]
\item \href{https://www.psgtech.edu/facgen.php?id=C3150}{Dr. Latha R}, Assistant Professor,  Department of Applied Mathematics and Computational Science, PSG College of Technology, Coimbatore. Contact: \href{mailto:rla.amcs@psgtech.ac.in}{rla.amcs@psgtech.ac.in}
\item \href{https://www.linkedin.com/in/sharadha-ramanan-43bb4946/}{Dr. Sharadha Ramanan}, Principal Scientist, TCS Research, Chennai. Contact:\href{mailto:sharadha.ramanan@tcs.com}{sharadha.ramanan@tcs.com}
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
